### 2023-10-31 README.Rmd
updates

2. Build the docker image of the computing environment, by running the build script.

@@

>>>>

2. Build the docker image of the computing environment, by running the build script. This will also build the apptainer image needed on HPC.

@@

On beluga, we use the apptainer iamge instead.

```{bash eval=FALSE}
. /workspace/conda/etc/profile.d/conda.sh 
. /workspace/conda/etc/profile.d/mamba.sh
PATH="$PATH:$HOME/.local/bin"
mamba activate cameratraps-detector
rofcamtrap/scripts/bash/camtrap.sh -b "/workspace/git" -s "/workspace/storage/my_passport_images" -m "/workspace/models/md_v5a.0.0.pt" md
```
